---
title: "First example"
output: learnr::tutorial
runtime: shiny_prerendered
params:
  id: dog-leap-hose
---

```{r dog-leap-house-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
learnr::tutorial_options(exercise.timelimit = 60, 
                 exercise.checker = gradethis::grade_learnr)
```
```{r context="setup", include=FALSE}
### Boilerplate: always include these packages
library(learnr)
library(gradethis)
library(etude2)
```

```{r context="setup", include=FALSE}
# Good practice to include these in any document bringing
# with the answer submission system
etude2::set_master_id("DD22")
etude2::etude_document_name("DD22")
# This can only be constructed after the document is complete
# You can get the names from the first column of the submission
# table (after you have made an entry for each item)
# The purpose here is to show the student a complete list of all
# of the questions in the document, so they can see at a glance what
# they are missing.
# If this isn't here, the submission table will not include 
# questions for which no answers has been submitted.
document_roster <- tibble::tribble(
  ~ id,
"DD22-3-aquiz", "DD22-4-bquiz", "DD22-1-first-question",
"DD22-2-from_etude", "DD22-5-multiple", "DD22-6-multiple2",
"ex1","ex3"
)
```




## Exercises

```{t ex1, exercise=TRUE}
2 + 2
```

```{r ex1-check}
grade_result(
  pass_if(~ .result == 19)
)
```

```{r ex3, exercise = TRUE, exercise.cap="Foofoo"}
3 + 4
paste("boo", "bah")
19
```

```{r ex3-check}
grade_result(
  pass_if(~ .result == 19)
)
```

## Questions

I don't need a special type for text entry. I just have to set the `incorrect` argument to `NULL` and give something sensible for the `try_again_button`. BUT, I DO HAVE TO CHANGE IT TO A textAreaInput() in the initialization code.

```{r textentry, eval=FALSE}
#question_text("What do you think about this?", answer("nice", correct=TRUE), allow_retry=TRUE, incorrect=NULL, try_again_button = "Edit answer.", placeholder = "Write a nice essay, please!")
```


```{r first-question}
etudeEssay("What do you think about this?",
           placeholder = "Write a nice answer")
```


```{r from_etude}
etudeEssay("What do you have to say about the electoral college?")
```

```{r aquiz, echo=FALSE}
etudeQ("How much?", 1:4, right_one=3, id="DD31:17", allow_retry=TRUE)
```

```{r bquiz}
etudeQ("Now how much?", 3:6, right_one=3, allow_retry=TRUE)
```

```{r multiple, echo=FALSE}
etudeQ("Which ones?", "+A+", "B", "C", "D", "+E+", allow_retry = TRUE,
       allow_multiple_correct = TRUE)
```

```{r multiple2, echo=FALSE}
etudeQ("Which ones are vowels?", 
       "+A+", 
       "B" = "B is a consonant.\n", 
       "C"="C is another consonant\n", 
       "D"="D is still another\n", 
       "+E+", 
       allow_retry = TRUE,
       allow_multiple_correct = TRUE)
```

## Hand in

This is the answer submission logic. Include a section like this *only* 
in top-level documents, not in individual problem files.


```{r context="server"}
current_state <- shiny::eventReactive(input$get_state, {
  All <- learnr:::get_objects(session)
  objs = learnr:::get_all_state_objects(session)
  objs = learnr:::submissions_from_state_objects(objs)
  
  return(objs)
})
current_state_report <- reactive({
  state_objs <- current_state()
  if (length(state_objs) == 0) return(tibble(message="No submissions yet"))
  condense <- function(item) {
    if (item$type == "exercise_submission") {
      tibble::tibble(id = item$id, 
                     question = "codebox",
                     answer = item$data$code,
                     time = as.character(Sys.time()), 
                     correct = if (item$data$checked) item$data$feedback$correct else FALSE,
                     attempts = 999
      )
    } else { # exercise submission
    tibble::tibble(id=item$id, 
                   question  = substr(item$data$question, 0, 20),
                   answer=item$data$answer,
                   time = as.character(item$data$time),
                   correct = item$data$correct,
                   attempts = length(item$data$history)/2
                  )
    }
  }
  For_report <- lapply(state_objs, condense) %>%
    dplyr::bind_rows()
  
  if (exists("document_roster")) {
    cat("Roster exists\n")
    For_report <- For_report %>% 
      dplyr::full_join(document_roster, by = "id")
  }

  For_report %>% 
    mutate(document = etude2::etude_document_name()) %>%
    arrange(id)
  
})
output$current_answers <- renderTable({current_state_report()})
output$hash_output <- renderText({
   paste(names(input), collapse="\n")
  # Logic to convert this to a CSV
  zz <- textConnection("forcsv", "w")
  write.csv(na.omit(current_state_report()),
            file=zz, row.names = FALSE)
  close(zz)

  learnrhash::encode_obj(paste(forcsv, collapse="\n"))

 })
```

```{r state, echo=FALSE}
shiny::actionButton("get_state", "Refresh summary of responses")
learnrhash:::wrapped_verbatim_text_output("hash_output", TRUE)
shiny::tableOutput("current_answers")
```





`r params$id`

