---
title: "An `{etude2}` Mother document"
output: learnr::tutorial
runtime: shiny_prerendered
params:
  id: mother1
---

This is an example of a "mother" document using `{etude2}`. Mother documents are those that:

1. Provide the submission widgets and logic for providing a report of a student's progress.
2. Cache the student's process (typically in the browser) using the `{learnr}` mechanism and recover the state when the session is renewed. (This means that students should not share a browser, unless they are working as an intended group.)
3. Optionally transclude `{etude2}` child documents, which are `{learnr}` documents *without* the submission widgets and logic. Such child documents are generally fully fledged `{learnr}` documents that can be compiled and run on their own. Note that mother documents should not be transcluded in other mother documents (as of this writing).

The next chunk sets up the `{gradethis}` system to work with the mother document. This is needed *only* if you are not transcluding a child document that does this for you. If you are mixing tutorial material that's contained directly in the mother document (as opposed to being transcluded from an `{etude2}` child) or material in a `{learnr}` document that doesn't use `{etude2}`, be careful that the `learnr::tutorial_options()` are set appropriately in this document.

```{r mother1-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
learnr::tutorial_options(exercise.timelimit = 60, 
                 exercise.checker = gradethis::grade_learnr)
```

The following chunk loads key libraries for the system. The chunk is in `context="setup"` so that these libraries are available both at compile time of the document and at run time.

```{r context="setup", include=FALSE}
### Boilerplate: always include these packages
library(learnr)
library(gradethis)
library(etude2)
```

In order for transcluded `{learnr}` "questions" to be associated with this document, the `master_id()` and `etude_document_name()` are set. The first prepends the id to the name/label/id of any question created with `etudeQ()` or `etudeEssay()` (and `{etude2}` functions later on, should they be created)

The `document_roster` This can only be constructed after the document is complete
You can get the names from the first column of the submission
table (after you have made an entry for each item)
The purpose here is to show the student a complete list of all
of the questions in the document, so they can see at a glance what
they are missing.

If `document_roster` isn't here, the submission table will not include questions for which no answers has been submitted. This isn't a disaster, but it can be nice for the scoring summary to show a student what has not yet been done. 

On the other hand, if question names are included in the roster without a matching question in the document, unnecessary lines will be added to the scoring summary which might cause fruitless searching by the student for those items.

```{r context="setup", include=FALSE}
# Good practice to include these in any document bringing
# with the answer submission system
etude2::master_id("M1")
etude2::etude_document_name("Mother1")

# 
document_roster <- tibble::tribble(
  ~ id,
"DD22-3-aquiz", "DD22-4-bquiz", "DD22-1-first-question",
"DD22-2-from_etude", "DD22-5-multiple", "DD22-6-multiple2",
"ex1","ex3"
)
```

## Using etude2 child documents


```{r child=file.path("/Users/kaplan/KaplanFiles/Packages/etude2/inst/ChildDocuments", "Basic/Basic.Rmd")}

```

## Questions

```{r first-question}
etudeEssay("What do you think about this?",
           placeholder = "Write a nice answer")
```


```{r from_etude}
etudeEssay("What do you have to say about the electoral college?")
```

```{r aquiz}
etudeQ("How much?", 1:4, right_one=3, id="DD31:17", allow_retry=TRUE)
```

```{r bquiz}
etudeQ("Now how much?", 3:6, right_one=3, allow_retry=TRUE)
```

```{r multiple}
etudeQ("Which ones?", "+A+", "B", "C", "D", "+E+", allow_retry = TRUE,
       allow_multiple_correct = TRUE)
```

```{r multiple2}
etudeQ("Which ones are vowels?", 
       "+A+", 
       "B" = "B is a consonant.\n", 
       "C"="C is another consonant\n", 
       "D"="D is still another\n", 
       "+E+", 
       allow_retry = TRUE,
       allow_multiple_correct = TRUE)
```



## Exercises

Regretably, `{learnr}` exercises are not yet integrated into the `{etude2}` naming system. Their names appear as the raw chunk names, for instance `ex1` and `ex3` here.



```{t ex1, exercise=TRUE}
2 + 2
```

```{r ex1-check}
grade_result(
  pass_if(~ .result == 19)
)
```

```{r ex3, exercise = TRUE, exercise.cap="Foofoo"}
3 + 4
paste("boo", "bah")
19
```

```{r ex3-check}
grade_result(
  pass_if(~ .result == 19)
)
```



## Hand in

This is the answer submission logic. Include a section like this *only* 
in mother documents, not in individual problem files.

```{r child=system.file("submission-handler.Rmd", package="etude2")}

```



-----

Document ID: `r params$id`

Location: `r knitr::current_input(dir = TRUE)` `r etude2::etude_document_name("Mother1")`

