---
title: "Daily Digital XXX"
subtitle: "Math 142Z"
date: "Due MMM DD YYYY"
output: learnr::tutorial
runtime: shiny_prerendered
tutorial:
  version: 0.1
tags:
- vectors
---


```{r mother1-setup, include=FALSE}
# Calculus/graphics/data packages
library(mosaic)
library(mosaicCalc)
library(ggformula)
library(math141Z)
knitr::opts_chunk$set(echo = FALSE)
learnr::tutorial_options(exercise.timelimit = 60, 
                 exercise.checker = gradethis::grade_learnr)
```


```{r context="setup", include=FALSE}
### Boilerplate: Packages relating to `{learnr}` and 
### submission functionality.
library(learnr)
library(gradethis)
library(etude2)
```



```{r context="setup", include=FALSE}
# Good practice to include these in any document bringing
# with the answer submission system
etude2::set_master_id("DD-") # Add the DD number
etude2::etude_document_name("DD-y") # Add the DD number
# Fill this data frame in when document is completed. See etude2 documentation
document_roster <- tibble::tribble(
  ~ id,
)
# Leave this safety check here
if (etude2::etude_document_name() == "DD-") 
  stop("You must set the master_id() and the document name specifically and uniquely for this document")
```

Anything that appears above the first section marker will be displayed on each page.

## Section 1

You can simply delete all of this text

## Section 2

You can delete this line, BUT NOT ANYTHING AFTER.


## Hand in your work

PRESS THE REFRESH BUTTON before copying the hash code and submitting it at the [USAFA Math 142Z site](https://forms.microsoft.com/Pages/ResponsePage.aspx?id=Bgq4einwwEWE0X2tGc48YcCKijCKVrhDla481YPh1UJUMVdERUtVT0VOSEpMMEdPQU1aWlpYTTA0RS4u)


```{r child=system.file("submission-handler.Rmd", package="etude2")}

```


-----

Location: `r knitr::current_input(dir = TRUE)` `r etude2::etude_document_name("Mother1")`

